%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers

% My packages
\usepackage{hyperref}
% Quotes
\usepackage{csquotes}
% Pretty pictures
\usepackage{graphicx}

\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Aalto University, School of science} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge  Three naive Bayes approaches for discrimination-free classification \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Sergio Isidoro} % Your name
\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Problem Overview}

The paper being analysed, , proposes 3 naieve bayes methods for discrimination free classification. For benchmarking, the paper uses the data set provided by UCI Machine learning repository \ref{uc_repo} on the Census data, trying to predict if an individual has high or low income (>=50 or <50)
This work aims to review and replicate the results of the paper and its' methods.

\section{The discrimination measure}

The discrimination measeure, and the algorithm later on it based, are slightly flawed. The discrimination measure is described as:
\begin{displayquote}
A simple solution is the discrimination score, which we define as the difference between the probability of a male and a female of being in the high-income class
\end{displayquote}
First of all, this leads to an asymetric concept of discrimination (we assume an a priory knowledge that the discrimination hapens only in the class \textit{female}). In the first algorithm we see that the optimization criteria is \textit{while discrimination > 0}, leading to the possibility of the algorithm reaching a discrimination that is negative, ie. positive discrimination to the previously discriminated class.
 
Also, this discrimination measure is sensitive to population size and bias. Let's say that all men access credit, and only the most successful women access credit. This measure would assume that the probabilty of a men accessing credit should be the same as the probability of women accesing credit, which will still discriminate women that are successfull and trying to access credit. 

The first problem could be solved by adding a conter measure for the case the discrimination goes bellow zero, instead of halting on 0.
The second problem is more difficult to tackle, but other work in this area try to \textbf{TODO TODO TODO}

\section{Methods}
The methods used were as closely replicated to the methods in \ref{calders10} as possible. For discretization of variables, values were ranked into 4 bins (analogous to very low, low, high, very high), but further processing of the bins, used in \ref{calders10} was discarted. There is no reference to data cleaning (althoug that reference is made in the benchmarks of the data set \ref{dataset}), so no action was taken to remove rows with missing atrributes. The missing attibutes were, instead, used as an attribute itself (with value "?"). 

\section{Results}


BAYES MODEL:

Accuracy: 78.4165591794 

Discrimination score: 0.398512741018 


2M MODEL:
Accuracy: 78.5332596278 
Discrimination score: 0.165316892258 

%------------------------------------------------

\begin{thebibliography}{9} 

\bibitem{paymentreport2014} \emph{World Payments Report 2014}, CapGemini, Royal Bank of Scotland, 2015.

\bibitem{uc_repo} \emph{{UCI} Machine Learning Repository}
M. Lichman, 2013, http://archive.ics.uci.edu/ml , University of California, Irvine, School of Information and Computer Sciences


\end{thebibliography}

\end{document}